### 2018-04-30 paper/security-discussion.tex

Alice wants to prevent Bob from learning which are her devices (as defined in 
\cref{system-model}).
Bob is allowed to infer the behaviour of devices in the Global Device Retinue, 
but a file transfer from Alice should not give Bob any information about which 
devices are Alice's.

Bob constructs \iac{SPOR} route that he gives to Alice.
This means that Alice does not learn any of Bob's destination devices.
When Alice starts sending the message, she will not connect directly to the 
device at the head of the route, since that might be Bob's device.
Alice will construct her own \ac{SPOR} route.
Thus Alice's devices are hidden from Bob's observation and vice versa.
If we assume that Alice and Bob can sample their nodes uniformly randomly from 
the \emph{entire} Global Device Retinue (we will return to this assumption 
below), then their probability of successful attack is proportional to their 
size in the network, \ie \(\frac{|D_i|}{|D|}\), for \(i\in \{a,b\}\).

Alice and Bob also want to prevent Carol and David to learn that Alice sent a 
message to Bob (as defined in \cref{system-model}).
Alice and Bob construct their \ac{SPOR} route by including devices from the 
Global Device Retinue, which also includes devices from Carol and David.
If all devices on the route belong to Carol and David, then they can, of course, 
learn that Alice sent a message to Bob.
How well they can do if they do not control the entire route, depends on the 
choice of the encryption scheme \(\Enc*\), used to encrypt the message \(m\) 
(see \cref{sec:file_exchange}).

@@

Many attacks against anonymous communications systems target the peer sampling 
mechanism, \eg~\cite{%
  RouteFingerprinting,%
  EpistemicAttacksOnRouteSelection,%
}.
So, even if our system is secure in theory, it will not be secure in practice 
unless the random peer sampling algorithm returns peers chosen uniformly 
randomly from the entire Global Device Retinue.

@@

\subsection{Future Work}
%
% \commentAL{To rewrite as real paragraphs} Future work and prospects:
% \begin{itemize}
% 	\item More in-depth knowledge of the user's behavior would allow to predict devices connections farther in the future;
% 	\item Changing devices' asymmetric keys regularly would increase security.
% 	Updating keys is easy in \name given the RPS that propagates new information to all nodes.
% 	However, more reflection would be needed to avoid key updates breaking ongoing communications passing through the devices in question;
% 	\item \name is not resilient to Byzantine nodes for now: malicious users could potentially make users pick Predictive Onion Routes that pass through them with a high probability, thus allowing the attacker to learn the file sender and receiver. To circumvent this, we would need to employ a secure Random Peer Sampling \cite{Jesi_Montresor_van_Steen_2010}, and prevent devices to lie on their probability of being online.

% \end{itemize}

>>>>

Alice wants to prevent Bob from learning which are her devices (as defined in 
\cref{system-model}).
Bob is allowed to infer the behaviour of devices in the global set, % Global Device Retinue, 
but a file transfer from Alice should not give Bob any information about which 
devices are Alice's.

Bob constructs \iac{SPOR} route that he gives to Alice.
This means that Alice does not learn any of Bob's destination devices.
When Alice starts sending the message, she will not connect directly to the 
device at the head of the route, since that might be Bob's device.
Alice will construct her own \ac{SPOR} route.
Thus Alice's devices are hidden from Bob's observation and vice versa.
If we assume that Alice and Bob can sample their nodes uniformly randomly from 
the \emph{entire} global set of devices %Global Device Retinue 
(we will return to this assumption 
below), then their probability of successful attack is proportional to their 
size in the network, \ie \(\frac{|D_i|}{|D|}\), for \(i\in \{a,b\}\).

Alice and Bob also want to prevent Carol and David to learn that Alice sent a 
message to Bob (as defined in \cref{system-model}).
Alice and Bob construct their \ac{SPOR} route by including devices from the 
global set %Global Device Retinue
, which also includes devices from Carol and David.
If all devices on the route belong to Carol and David, then they can, of course, 
learn that Alice sent a message to Bob.
How well they can do if they do not control the entire route, depends on the 
choice of the encryption scheme \(\Enc*\), used to encrypt the message \(m\) 
(see \cref{sec:file_exchange}).

@@

Many attacks against anonymous communications systems target the peer sampling 
mechanism, \eg~\cite{%
  RouteFingerprinting,%
  EpistemicAttacksOnRouteSelection,%
}.
So, even if our system is secure in theory, it will not be secure in practice 
unless the random peer sampling algorithm returns peers chosen uniformly 
randomly from the entire global set. %Global Device Retinue.

@@

\subsection{Future Work}
